Preliminary Thesis Defence

### 2013-12-14 PTD.tex
add ms model

However, the authors then proceed to introduce a measure of risk around perceptions by investors.
Investors thus do not now the actual state of the fundamentals, but rather a distored form of it.
As a result, the investors' perception of other investors' perceptions are even more distorted.
Paradoxically, the leads to model being solvable to a unique equilibrium.

\section{The Model}

>>>>

However, the authors then proceed to introduce a measure of risk around perceptions by investors.
Investors thus do not know the actual state of the fundamentals, but rather a distored form of it.
As a result, the investors' perception of other investors' perceptions are even more distorted.
Paradoxically, the leads to model being solvable to a unique equilibrium.

\section{The Model}
I will give a brief description of the model as it is defined, and some it features.
There is a state of economic fundamentals $\theta$ which is distributed as $\theta \sim U[0,1]$.
The exchange rate is the hypothetical situation of no government intervention is a function only of these fundamental ($f(\theta)$),
it is assumed that $\frac{\partial f}{\partial \theta} > 0$.
The currency is pegged at a level larger than that derived from the fundamentals ($e* \geq f(\theta)$).
Speculators can short the currency at a cost $t$, their payoff is thus $e* - f(\theta) - t$.
